Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
another par

Luckily, we can avoid all of these problems at once if we have a single,
executable specification of what exactly a programs input is supposed
to look like. In fact, definitive grammars have long been written for
all sorts of protocols and are the standard way of describing text-based
protocols.  Parser generators can automatically create parsers for such
languages, and with common classes of grammars such as regular expressions
or deterministic context free languages, that parser can be expressed
in a computationally less powerful form, e.g. a finite automaton or a
push down automaton, limiting the weird machine problem and enabling
very efficient implementation~\cite{Knuth1965607}.

Specifications of binary protocols, such as RFCs, also contain grammars,
although they are frequently translated into prose and diagrams as
opposed to the traditional Backus-Naur-Form.

>>>>

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to build a tool for
parsing inputs given a particular grammar, such as the traditional {\tt
lex} and {\tt yacc} generators.  Applications that use such a tool to
process input data will not need to write error-prone input processing
code, and as long as the tool is bug-free, the application will be safe
from input processing vulnerabilities.

### 2014-04-01 paper/relwk.tex
another par

Finally, many protocol implementations are so complicated that even
without bugs, they inadvertently provide a full Turing-complete execution
environment. Examples include X86 page tables~\cite{bangert2013page},
ELF symbols and relocations~\cite{shapiro2013weird}. Even though
these protocols were never intended to be that expressive -
and consequentially hard to parse, implementation details of their
recognisers - which de facto became a part of the specification and were
relied upon by legitimate inputs - expose unwanted computational power
and have unintended side-effects.  In the offensive research community,
this has been generalised into treating a program as a \textit{weird
machine}~\cite{bratus2011exploit} that operates on an input, analogous
to a virtual machine operating on bytecode.

@@

>>>>

Many protocol implementations are so complicated that even
without bugs, they inadvertently provide a full Turing-complete execution
environment. Examples include X86 page tables~\cite{bangert2013page},
ELF symbols and relocations~\cite{shapiro2013weird}. Even though
these protocols were never intended to be that expressive -
and consequentially hard to parse, implementation details of their
recognisers - which de facto became a part of the specification and were
relied upon by legitimate inputs - expose unwanted computational power
and have unintended side-effects.  In the offensive research community,
this has been generalised into treating a program as a \textit{weird
machine}~\cite{bratus2011exploit} that operates on an input, analogous
to a virtual machine operating on bytecode.

Parser generators can automatically create parsers for such languages,
and with common classes of grammars such as regular expressions or
deterministic context free languages, that parser can be expressed in a
computationally less powerful form, e.g. a finite automaton or a push
down automaton, limiting the weird machine problem and enabling very
efficient implementation~\cite{Knuth1965607}.

@@

In fact, definitive grammars have long been written for all sorts of
protocols and are the standard way of describing text-based protocols.
Specifications of binary protocols, such as RFCs, also contain grammars,
although they are frequently translated into prose and diagrams as
opposed to the traditional Backus-Naur-Form.
